### 2019-08-09 README.Rmd
Updates to the README Added acknowledgement - closes #36 Automated creation of the rob_traffic_light() image

## Description
```{r include = FALSE}
library(robvis)
library(kableExtra)
library(magrittr)
```
The `robvis` package takes the summary table from risk-of-bias assessments, converts it to tidy data, and produces summary plots formatted according to the assessment tool used.

@@

```{r eval=FALSE}
trafficlight_rob <- rob_traffic_light(data = data_rob2, tool = "ROB2")
trafficlight_rob
```    
<img src="man/figures/rob2trafficlight.png" width="70%" height="70%"/>

@@

* [Emily Kothe](https://github.com/ekothe) for help in fixing `ggplot2` coding issues.
* [Eliza Grames](https://github.com/elizagrames) for creating the `robvis` hex sticker.

>>>>

## Description
```{r include = FALSE}
library(robvis)

library(kableExtra)
library(magrittr)
```
The `robvis` package takes the summary table from risk-of-bias assessments, converts it to tidy data, and produces summary plots formatted according to the assessment tool used.

@@

```{r, eval=FALSE}
trafficlight_rob <- rob_traffic_light(data = data_rob2, tool = "ROB2")
trafficlight_rob
```

``` {r, include=FALSE}
trafficlight_rob <- rob_traffic_light(data = data_rob2, tool = "ROB2")
ggplot2::ggsave(
          "man/figures/rob2trafficlight.png",
          plot = trafficlight_rob,
          device = "png",
          width = 6,
          height = 9,
          units = "in",
          dpi = 800, 
          limitsize = FALSE)
```
<center><img src="man/figures/rob2trafficlight.png" width="70%" height="70%"/></center>

@@

* The `rob_summary()` function was based on code forwarded by a colleague. I have recently learnt that this code was adapted from the wonderful "[Doing Meta-Analysis in R](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/)" guide, so I would like to retrospectively acknowledge the authors for their indirect help. 
* [Emily Kothe](https://github.com/ekothe) for help in fixing `ggplot2` coding issues.
* [Eliza Grames](https://github.com/elizagrames) for creating the `robvis` hex sticker.
